Enter our title here

### 2017-09-25 manuscript.tex

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
unfold, the use of statistical software has become increasingly emphasized in education (**do i need to cite this**). By integrating the
capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
interpreting real data sets \cite{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
classroom \citet{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
to use technology "as a way to explore conceptual ideas and enhance student learning" \cite{AmericanStatisticalAssociation2016}.

@@

\begin{verbatim}
devtools::install_version("ggplot2", "2.2.0")
devtools::install_version("mosaic", "0.14.4")
\end{verbatim}
In order for `DataCamp' to recognize this new file, you will need to add $$from: r-base-prod:27$$ to the course.yml file.

**How do I override the subscripts for devtools?**

@@

%Use this for final submission
%\bibliographystyle{ECA_jasa}
\bibliographystyle{Chicago}
\bibliography{library}
% before it was 'library' so I thought if I changed it to the new bib file it would work but it doesn't :(

>>>>

3) were you going to set something up on here that i was going to fill in? Oh the R code boxes where I can add the DataCamp edit code
It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
unfold, the use of statistical software has become increasingly emphasized in education (**do i need to cite this**). By integrating the
capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
classroom \citep{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
to use technology "as a way to explore conceptual ideas and enhance student learning" \citep{AmericanStatisticalAssociation2016}.

@@

\begin{verbatim}
devtools::install_version("ggplot2", "2.2.0")
devtools::install_version("mosaic", "0.14.4")
\end{verbatim}
In order for DataCamp to recognize this new file, you will need to add \texttt{from: r-base-prod:27} to the \texttt{course.yml} file.

@@

%Use this for final submission
%\bibliographystyle{ECA_jasa}
\bibliographystyle{ECA_jasa}
\bibliography{library}
% before it was 'library' so I thought if I changed it to the new bib file it would work but it doesn't :(
